\ZpL: a p-adic precision package

### 2017-11-17 ZpL/ZpL.tex
Added subsection "Correctness"
Added Section 4 to the plan

\usepackage{amsmath,amssymb}
%\usepackage{amsthmnoproof}
\usepackage{amsthm}
\usepackage{mathrsfs}
%\let\bibsection\relax
%\usepackage{amsrefs}
%\usepackage[usenames,dvipsnames]{color}
\usepackage{stmaryrd}
\usepackage{enumerate}
%\usepackage[algoruled,vlined,english,linesnumbered]{algorithm2e}
%\usepackage[pdfpagelabels,colorlinks=true,citecolor=blue]{hyperref}
\usepackage{comment}
\usepackage{multirow}
%\usepackage{tikz}

@@

\newcommand{\ZpL}{\texttt{ZpL}}
\newcommand{\ZpLCA}{\texttt{ZpLCA}}
\newcommand{\ZpLCR}{\texttt{ZpLCR}}
\newcommand{\ZpLF}{\texttt{ZpLF}}

@@

\title{ZpL: a p-adic precision package}

@@

\begin{itemize}
\item Elementary arithmetic
\item Determinant + matrix multiplication
\item gcd of polynomials
\item some benchmarks on precision
\end{itemize}

@@

@@

>>>>

\usepackage{amsmath,amssymb}
%\usepackage{amsthmnoproof}
\usepackage{amsthm}
\usepackage{mathrsfs}
%\let\bibsection\relax
%\usepackage{amsrefs}
%\usepackage[usenames,dvipsnames]{color}
\usepackage{stmaryrd}
\usepackage{enumerate}
%\usepackage[algoruled,vlined,english,linesnumbered]{algorithm2e}
%\usepackage[pdfpagelabels,colorlinks=true,citecolor=blue]{hyperref}
\usepackage{comment}
\usepackage{multirow}
\usepackage{xspace}
%\usepackage{tikz}

@@

\newcommand{\ZpL}{\texttt{ZpL}\xspace}
\newcommand{\ZpLCA}{\texttt{ZpLCA}\xspace}
\newcommand{\ZpLCR}{\texttt{ZpLCR}\xspace}
\newcommand{\ZpLF}{\texttt{ZpLF}\xspace}

@@

\title{\ZpL: a p-adic precision package}

@@

\subsection{Elementary arithmetic}

\begin{itemize}
\item Compare $px$ and $x + x + \cdots +x$ ($p$ times)
\item Compare $x^p$ and $x \cdot x \cdots x$ ($p$ times)
\item $x$ and $y$ are given at different precision, compute $u = x+y$,
$v = x-y$ and $u+v$
\end{itemize}

\subsection{Linear algebra}

\begin{itemize}
\item determinant
\item characteristic polynomial
\end{itemize}

\subsection{Commutative algebra}

\begin{itemize}
\item gcd of polynomials
\end{itemize}

@@

\subsection{Correctness}

\begin{itemize}
\item prove that \ZpLCA and \ZpLCR are correct under some assumptions
(to be determined)
\item explain that \ZpLF is not meant to provide proved results
\end{itemize}

@@

\section{Presentation of the package}

\begin{itemize}
\item How to access to the precision
\item Diffused digits
\item Historic of variables creation/deletion, etc...
\item Other features?
\end{itemize}

\subsection{More examples}

\begin{itemize}
\item SOMOS sequence
\item many multiplications of matrices
\item Dodgson algorithm
\item subresultants
\item Grobner basis
\item $p$-adic differential equations
\end{itemize}
